Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow

### 2009-04-29 paper/paper.tex
Small bugfix with zip file time. Started to work on reviewer comments.

Currently the HTTP Stream is read only, but in future we anticipate
write support to be implemented, for example, using the WebDav
extensions to HTTP\cite{webdav-rfc}. The HTTP stream also supports the
File Transfer Protocol (FTP) and HTTPS (Secure Sockets Layer---SSL)
protocols transparently. This support is provided automatically by the
curl library.

@@

\section{Usage Scenarios}
In this section we describe how AFF4 may be used in various
situations. Many of those can be solved using other forensic file
formats, but often in a more awkward way.

@@

\subsection{Logical File Acquisition}
Sometimes in a forensic investigation it is impossible to take a true
forensic image of the underlying disk, and we must resort to acquiring
discrete files instead. Such a case might occur for example, when
investigating an incident on a very large network storage system or a
critical system which can not be brought down for the duration of the
image acquisition.

It is still advantageous in this case to bring these files into the
AFF4 evidence universe by acquiring each evidence file using a unique
URN. As explained in \ref{definitions}, segments are AFF4 stream
objects which are implemented by storing the data in Zip archive
members. It follows, therefore, that a regular zip file containing
files is also a valid AFF4 volume providing the segment names are
globally unique.

So a logical image of files, can be created by any regular Zip
compression program in the field. Once brought into the lab these
volumes can be given a volume URN and imported into the Universal
Resolver to provide access to all the files within the archive.

@@

This paper describes a significant enhancement to Garfinkel's Advanced
Forensic Format (AFF1). The new version, AFF4, offers significant new
features including the ability to store multiple kinds of evidence
from multiple devices in a single archive, and an improved separation
between the underlying storage mechanism and forensic software that
makes use of evidence stored using AFF. This improved system will
allow a single archive of evidence to be used in a plethora of
modalities, including in a single evidence file, multiple evidence
files stored on multiple workstations, and evidence stored in a
relational database or object management system---all without making
changes to forensic software.

We have an initial implementation of AFF4 working in the lab and plan
to integrate it into Garfinkel's. After integration and testing, we
plan to release this system as freely usable open source software.

>>>>

Our implementation also enables direct writing to a HTTP URL using the
WebDav extensions to HTTP\cite{webdav-rfc}. The HTTP stream also
supports the File Transfer Protocol (FTP) and HTTPS (Secure Sockets
Layer---SSL) protocols transparently. This support is provided
automatically by the curl library.

@@

\section{Usage Scenarios}
In this section we describe how AFF4 may be used in various
situations. Since the AFF4 framework implements a distributed evidence
management system, we demonstrate its use by a fictitious
multinational corporation with offices in Los Angeles and New
York. Each office has its own computer forensics lab and is connected
via a WAN.

\subsection{Using distributed evidence}
An investigation is conducted by the New York team. The case relates
to a hard disk image stream stored inside a volume, in turn stored on
the NY evidence server at URL http://ny.wan/evidence1.aff4 . The team
requires an analyst (Bob) in LA to assist with their analysis. The LA
analyst types\footnote{fls is the file listing command which is part
of the Sleuthkit}:

\begin{lstlisting}
fls -i aff4 "NY case 1"
\end{lstlisting}
This command causes the local AFF4 implementation to:
\begin{enumerate}
\item Contact the universal resolver asking where \emph{``NY case 1''} is
stored.
\item The universal resolver replies that it is a symbolic link to a
stream called \emph{``urn:aff4:1234''} stored within the volume
\emph{``urn:aff4:9876''}. Further queries reveal that the volume is
located at \emph{http://ny.wan/evidence1.aff4}.
\item The local AFF4 library then directly accesses the volume at the
given URL. Note that the entire volume is not copied, instead specific
chunks are retrieved on an as needed basis.
\end{enumerate}

The overall effect is that the user in LA is able to directly access
the disk image specified using a friendly name, and stored at a remote
location easily.

\subsection{Load redistribution}
In the previous scenario, Bob becomes involved in this case, and
wishes to download the entire image locally to
\emph{http://la.wan/evidence1.aff4}. The Universal Resolver now has
two possible locations for the same volume URN, since there are two
copies in existence. Based on pre-determined distance metrics, the
resolver directs requests from Bob to the LA copy, while Alice is
redirected to the NY copy. This load redistribution can be used for
optimal management of evidence storage in a transparent way. Analyst
are not aware of where the evidence is physically stored, and it
appears as though all evidence is always available.

\subsection{Remote imaging}
The NY IT security team has just responded to an incident on one of
their servers. Alice, the responding officer, wishes to image the
server. She types:
\begin{lstlisting}
aff4imager -i -o http://ny.wan/evidence2.aff4 \
	-k http://ny.wan/alice.key \
	-c http://ny.wan/alice.crt /dev/sda
\end{lstlisting}

This command requests an image be created directly on the evidence
server (it will be uploaded using webdav). The image is signed using
Alice's certificate and key (which might need to be unlocked). Note
that Alice does not need any hardware to obtain the image as it is
done over the network - she therefore can respond rapidly.

Bob is an analyst in LA which specializes in filesystem analysis. As
soon as the acquisition is complete, the image is available for Bob to
examine. Bob does not have permissions to create volumes on the NY
evidence server, so he types:
\begin{lstlisting}
fsbuilder -o http://la.wan/evidence3.aff4 \
	http://ny.wan/evidence2.aff4
\end{lstlisting}
This creates a new volume on the LA server which contains a set of Map
streams referring to the original evidence. The new volume is near
zero cost but refers to the original image (which is still stored in
NY).

@@

\subsection{Logical File Acquisition}
Alice is responding to an incident on a critical corporate
server. Since the system can not be taken down for forensic imaging,
Alice must resort to acquiring discrete files instead. Alice is unable
to install and run any acquisition software on the server due to
policy restrictions.

It is still advantageous in this case to bring discrete files into the
AFF4 evidence universe by acquiring each evidence file using a unique
URN. As explained in \ref{definitions}, segments are AFF4 stream
objects which are implemented by storing the data in Zip archive
members. It follows, therefore, that a regular zip file containing
files is also a valid AFF4 volume.

So a logical image of files, can be created by any regular Zip
compression program in the field. Once brought into the lab these
volumes are given a volume URN and imported into the Universal
Resolver to provide access to all the files within the archive. At
this stage digital signatures can also be added for each logical file.

Alice uses windows explorer to obtain a Zip file of the files of
interest. After taking the file back to the lab, she then signs the
files, and adds a volume URN, making the Zip file a fully compliant
AFF4 volume.

@@

This paper describes a significant enhancement to the Advanced
Forensic Format (AFF1). AFF4, extends beyond a file format to describe
a universal framework for evidence management, offering significant
new features such as the ability to store multiple kinds of evidence
from multiple devices in a single archive, and an improved separation
between the underlying storage mechanism and forensic software that
makes use of evidence stored using AFF. This improved system allows a
single archive of evidence to be used in a plethora of modalities,
including in a single evidence file, multiple evidence files stored on
multiple workstations, and evidence stored in a relational database or
object management system---all without making changes to forensic
software.

We have developed an open source reference implementation, but the
AFF4 framework is simple enough for competing implementations to be
implemented commercially. We hope this simplicity enhances AFF4's
acceptance and adoption as a standard evidence management platform.
